Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-06 paper.tex
save

In this work, author disambiguation is cast into a semi-supervised clustering
problem, as inspired from several previous works described in Section~\ref
{related-works}. Our algorithm is made of four elements: (i) a blocking
function $b$ whose goal is to rhoughly pre-cluster signatures in order to
reduce computational complexity; (ii) the construction of a similarity function
$d$ between signatures using supervised learning algorithms; (iii) the
semi-supervised clustering of all signatures within a same block, using $d$; (iv) the matching
of predicted clusters to existing profiles in a database.

@@

% Our methodology consists in 4 main components: Distance learning, blocking,
% semi-supervised clustering and matching. A distance function is learned from a
% training set of signiture pairs sampled from ground-truth data. Each pair is
% labeled whether the 2 signatures are for the same real author or not. The
% learned distance function will then be used for computing the dissimilarity
% matrix of a block of signatures. A block of signatures is grouping signatures
% that have in common similar author names, for example same last name. This
% affinity matrix would be the main input of our semi-supervised clustering
% algorithm. The predicted clusters of each block will lastly be combined into a
% final predicted clusters result. Each cluster label represents the predicted
% single author of the publications in the cluster. Finally, we present a
% strategy for matching the predicted results with the publications in which
% their authors were claimed.

>>>>

In this work, author disambiguation is cast into a semi-supervised clustering
problem, as inspired from several previous works described in Section~\ref
{related-works}. Our algorithm is made of four elements: (i) a blocking
function $b$ whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
reduce computational complexity; (ii) the construction of a similarity function
$d$ between signatures using supervised learning; (iii) the
semi-supervised clustering of all signatures within a same block, using $d$; (iv) the matching
of predicted clusters to existing profiles in a database.

@@
